---
title: "OMSCS_Fall2016_DiscussionForum"
author: "Rui"
date: "October 21, 2016"
output: 
  html_document: 
    keep_md: yes
---

```{r}

library(jsonlite)
getwd()
setwd("/Users/ruihu/Documents/DataScience/Joyner_Data")
usersJson <- fromJSON("users.json") 
class_contentJson<-fromJSON("class_content.json")
names(class_contentJson)
class(class_contentJson)
changelog<-class_contentJson[['change_log']]
post_record<-class_contentJson[2,]
post_record
class(post_record[1,1])
str(post_record[1,1])
class(children)
class(changelog[1])
changelog[1]
names(changelog[[1]])
names(changelog[[2]])
changelog[[1]]

changelog[[7]]
children<-class_contentJson['children']
class(children[1,])
children[1,]
        
```
original data frame of content_json: each row is a post thread record. In this record, recorded each time when there is a new response, follow up, feedback, also recorded each response's author name, content, original post' author name, subject, contents. 

A flatened data structure need to have:
post thread ID: change_log$data
original thread subject and content: history$subject history$content
author of original thread: history$uid
published time: history$created

```{r,echo=TRUE}
library(dplyr)
usersJson <- fromJSON("users.json") 
names(usersJson)
class_contentJson<-fromJSON("class_content.json")
discussion_data<-data.frame(post_id=character(0), author=character(0), subject=character(0), content=character(0), type=character(0), when=character(0),stringsAsFactors=FALSE)
str(discussion_data)
discussion_data
for(i in 1:3){
  post_record<-class_contentJson[i,]
  post_record
  post_log<-post_record$change_log
  post_log
  
  post_replies<-post_record$children
  post_replies
  class(post_replies)
  class(post_replies[[1]])
 length(post_replies[[1]][[2]])
  post_id<-post_log[[1]][[1]][[1]]
  post_id
  class(post_record$history)
  author<-post_record$history[[1]][[1]]
  print(author)
  subject<-post_record$history[[1]][[4]]
  print(subject)
  content<-post_record$history[[1]][[3]]
  type<-post_record$type
  print(type)
  when<-post_log[[1]][[5]][[1]]
  class(when)
  c(post_id,author,subject,content,type,when)
  discussion_data
  discussion_data<-rbind(discussion_data,setNames(as.list(c(post_id,author,subject,content,type,when)),names(discussion_data)))
 discussion_data
 post_replies[[1]][[2]]
 length(post_replies[[1]][[2]])
 length(post_replies[[1]][[2]])
  for(j in 1:length(post_replies[[1]][[2]])){
    author<-post_replies[[j]][[8]]
    content<-post_replies[[j]][[16]]
    when<-post_replies[[j]][[13]]
    type<-post_replies[[j]][[7]]
   discussion_data<-rbind(discussion_data,setNames(as.list(c(post_id,author,subject,content,type,when)),names(discussion_data)))
   discussion_data
    for (k in 1:length(post_replies[[1]][[2]][[1]][[2]])){
      author<-post_replies[[1]][[2]][[1]][[7]][[k]]
      content<-post_replies[[1]][[2]][[1]][[14]][[k]]
      when<-post_replies[[1]][[2]][[1]][[11]][[k]]
      type<-post_replies[[1]][[2]][[1]][[6]][[k]]
    
      discussion_data<-rbind(discussion_data,setNames(as.list(c(post_id,author,subject,content,type,when)),names(discussion_data)))
      
    }
  }
  names(discussion_data)
  class(discussion_data$post_id)
  class(discussion_data$author)
  class(discussion_data$type)
}
```

```{r, echo=TRUE}
test<-do.call(c, unlist(class_contentJson, recursive=FALSE))
for(i in 1:1216){
  change_log_Name = paste("change_log", as.character(i), ".data",sep="")
  post_id<-test$change_log_Name[1]
  children_uid_Name=paste("children",as.character(i),".uid",sep = "")
  author<-test$children_uid_Name
}
```

subject<-post_record$historysubject // gettting the post subject
j<-length(children) 
for j in 1:length(children) // 
  author<-children$uid
  content<-children$subject
  
  
children is a list, including whatever amount of 1st level reply; each reply is a list too, including whatever amount of 2nd level reply
level1_reply<-


```
children posts content: children$subject
author of children: children$uid
published time:children$created/updated

For one post thread, the number of change_log should equal to number of children and children's children plus history. 
change_log$when should match with:
history$created
children$created/updated
children's children$created/updated



change_log$data: a post thread
change_log$uid: a behavior to a post: create/follow up/feedback
change_log$to: unknown, when exists, equals to id in content_json

children$uid is user_id in users.json
children$id: unknown
children$subject: content of the post

level 1 children: first level reply
level 2 children: 2nd level reply

history$uid: is user_id in users.json
history$content: original post content
history$subject: original post subject

$unique_views
